### 2021-12-10 docs/manuscript/manuscript.tex
Move list of legends for supporting info files after references list
Remove financial information from Acknow...
Remove address from Affiliations

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Elucidating multi-input processing 3-node gene regulatory
network topologies capable of generating striped gene expression patterns}
% Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Juan Camilo Arboleda-Rivera\textsuperscript{1*},
Gloria Machado-Rodríguez\textsuperscript{1},
Boris A. Rodríguez\textsuperscript{2},
Jayson Gutiérrez\textsuperscript{3},
\\
\bigskip
\textbf{1} Grupo de Fundamentos y Enseñanza de la Física y los Sistemas Dinámicos,
Instituto de Biología, Facultad de Ciencias Exactas y Naturales, Universidad de Antioquia
UdeA, Calle 70 No. 52-21, Medellín, Colombia.
\\
\textbf{2} Grupo de Fundamentos y Enseñanza de la Física y los Sistemas Dinámicos,
Instituto de Física, Facultad de Ciencias Exactas y Naturales, Universidad de Antioquia
UdeA, Calle 70 No. 52-21, Medellín, Colombia.
\\
\textbf{3} Flanders Marine Institute (VLIZ), Wandelaarkaai 7, 8400 Oostende,
Belgium
\\
\bigskip

@@

%\section*{Conclusion}

\section*{Acknowledgements}
The computational resources (Stevin Supercomputer Infrastructure) and
services used in this work were provided by the VSC (Flemish Supercomputer
Center), funded by Ghent University, FWO and the Flemish Government–department EWI.
All authors acknowledge partial support from CODI-Universidad de Antioquia under
project ``Estudio de la Evolución de Circuitos de Regulación del Desarollo
Embrionario a través de la Biología Evolutiva de Sistemas'' code 2017-14367. All
authors acknowledge the Colombian youth for their defense of a better country.

>>>>

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Elucidating multi-input processing 3-node gene regulatory
network topologies capable of generating striped gene expression patterns}
% Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Juan Camilo Arboleda-Rivera\textsuperscript{1*},
Gloria Machado-Rodríguez\textsuperscript{1},
Boris A. Rodríguez\textsuperscript{2},
Jayson Gutiérrez\textsuperscript{3}
\\
\bigskip
\textbf{1} Grupo de Fundamentos y Enseñanza de la Física y los Sistemas Dinámicos,
Instituto de Biología, Facultad de Ciencias Exactas y Naturales, Universidad de Antioquia
UdeA, Medellín, Colombia.
\\
\textbf{2} Grupo de Fundamentos y Enseñanza de la Física y los Sistemas Dinámicos,
Instituto de Física, Facultad de Ciencias Exactas y Naturales, Universidad de Antioquia
UdeA, Medellín, Colombia.
\\
\textbf{3} Flanders Marine Institute (VLIZ), Wandelaarkaai 7, 8400 Oostende,
Belgium
\\
\bigskip

@@

\section*{Acknowledgements}
The computational resources (Stevin Supercomputer Infrastructure) and
services used in this work were provided by the VSC (Flemish Supercomputer
Center), funded by Ghent University, FWO and the Flemish Government–department EWI.
All authors acknowledge the Colombian youth for their defense of a better
country.
